Regression Cube Analysis of Cohort Study Data

### 2015-03-30 draft.tex
revised application

We defined an Interactive Visual Analysis workflow for image-centric cohort study data, by extending the feature selection step (recall \ref{sec:Background}) with an iterative analysis loop incorporating group selection and visualization using expert input as well as clustering methods \cite{Klemm2014VIS}.
%%
Information visualizations of cohort study features were augmented with extracted image data, yielding linked views with both image and non-image information.
%% 
% erst die Erkl√§rung, dann die Folge daraus =)
The mosaic plot presented in \cite{Klemm2014VIS} highlights the pairwise correlation between features without a target disease by depicting the \emph{Cram\'{e}r's V} contingency values.
%%
Its great popularity among our domain experts was the inspiration for this work.
%%

@@

% nochmal checken wo $F$ eingef¸hrt wird, hier oder im ¸bern‰chsten Satz?

@@

% Ggf. wurde $F$ schon oben eingef¸hrt, TODO

@@

\paragraph{3D (Cube) View.}
%%
Introducing $Z$ creates a 3D \emph{Regression Cube} (Fig.~\ref{fig:Cube} b).
%%
$R^2$ values of each cube entry (\emph{voxel}) is mapped to opacity to reduce the overlap.
%%
The visualization of $R^2$ values derived from different regression cubes (e.g., $Z \sim X + Y$) is misleading, as they can be compared relatively, but not in precise numbers.
%%
% e.g. wenn man es w‰hlen kann
% i.e. wenn es so ist
Therefore, the $R^2$ results of different regression methods are encoded using different colors (i.e., blue for linear regression and red for logistic regression).
%%
% Adverb immer vors Hauptverb oder Satzende
Thus, the cube can be easily extended using other regression types.
%%
For cubes with a fixed target feature, e.g., $Cancer \sim X + Y + Z$, no such encodings are required and the $z$ dimension can be compared directly.
%%
\\\\
Our goal is to create an overview visualization for a data set, but we also want to incorporate expert knowledge into the visualization by adapting the underlying formulas.
%%
These two approaches do not exclude each other, they rather underline the difference in purpose of the chosen formula.
%%
The different analysis approaches require different starting points using the \emph{Regression Cube}.

\subsection{Analysis Workflow} \label{sec:Workflow}
%%
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.0in]{figures/workflow}
 \caption{
 Different workflow types of the analysis using \emph{Regression Cubes} (based on~\cite{Keim}).
 %%
 % The analysis starts with a set of features given by the data set.
 %%
 [\textbf{1.AF}] The workflow starts by declaring a formula regarding to specify a hypothesis, or use a predefined formula for a hypothesis-free analysis.
 %%
 [\textbf{2.SI}] The \emph{Regression Cube} is then visualized.
 %%
 The user has the option to either adjust the formula or to derive details on demand on a specific regression.
 %%
 [\textbf{3.ZF}] Insights into the data yield either an adjustment of the current formula or selecting a difference view.
 %%
 The latter is used to compare regression cubes.
 %%
 [\textbf{4.DD}] Details about features using the 2D mosaic plot representation yields insights and hypothesis about feature relations.
 }
  \label{fig:Workflow}
\end{figure}
%%
%\com{Different Formulas work as different steps in the analysis (Fig.~\ref{fig:Workflow})}
%\com{Workflow for different analysis approaches.}
%\com{0. Select the Variables.}
%\com{1. Select the Formulas}
%\com{a) Analysis without hypothesis about the data set (z ~ x+y)}
%\com{b) Analysis without hypothesis with confounder (z ~ age)}
%\com{c) Analysis with hypothesis about the data set (Var ~ x+y+z)}
%\com{d) Use Difference View}
%\com{d) Clarify using confounder (Var ~ x)}
%\com{3. Find interesting pane.}
%\com{4. Get Details on Demand.}
%%
% ‹bergang ist recht holprig gewesen
Our Regression Cube models is well-suited for different workflow analysis techniques, based on the Visual Analytics (VA) Mantra of Keim et al. \cite{Keim}:

@@

% warum war da ein "either", sollte der Satz etwas anderes ausdr¸cken?
Hypotheses about the data are easily built up by relating dynamic variables with the regression operators.
%%
Furthermore, static features can be added for each regression formula.
%%
Here are a few examples:

@@

\section{Application} \label{application}
%%
\begin{figure*}[htb]
 \centering
 \includegraphics[width=7.0in]{figures/application}
 \caption{
 The analysis of the numerical and dichotomized target feature depicting liver-fat values yields similar results (left).
 %%
 In (a), hot spots for somatometrical features with high correlations were found.
 %%
 High correlations were also found for features depicting \emph{hepatic steatosis} (b).
 %%
 A high correlation between \emph{Interleukin-6}, \emph{hepatic steatosis}, \emph{GGT} and \emph{Lipase} (highlighted using arrows) was revealed during the analysis using the 2D mosaic plot.
 %%
 \com{Caption Breast Fat Data}
 }
  \label{fig:Application}
\end{figure*}
%%
In this section, we describe how we applied the \emph{Regression Cube} to two epidemiological data sets.
%%
The hepatic steatosis data set was analyzed using data mining algorithms, yielding risk groups, which we now analyze further.
%%
Also, we try to reproduce the prior results from this analysis as proof-of-concept of our method.
%%
The breast fat data set is the foundation for an explorative analysis towards the influencing parameters of the parenchyma tissue of the female breast.
%%

@@

The \textbf{1.AF} was started by \emph{KH} using the default formula for hypothesis-free analysis ($Z \sim X + Y$).
%%
At first, she was interested in correlations with the parenchyma tissue segmentations, which was selected through the drop-down for the z-axis (\textbf{2.SI}).
%%
She observed expected strong correlations with age, body fat percentage, hip and waist circumference
as well as menstrual period or pregnancy status.
%%
Fat women also have a larger breast fat percentage, which also correlates with other somatometric features.
%%
Age is a strong influencing factor, as breast tissue degrades over time and subsequently the parenchyma tissue.
%%
\emph{KH} proceeded using [\textbf{2.SI}] and [\textbf{3.DD}] to check for relationships for different target features, such as current hormone replacement therapy, BI-RADS (classification of the mammography findings) as well as different diseases, such as diabetes or gout.
%%
She observed relationships matching her expectations and expert knowledge.
%%
One unexpected relationship was observed between mammography lesions and menstruation cycle towards spiral contraception were observed ($R^2$ of $0.77$).
%%
\emph{KH} proceeded with a detailed analysis of the parenchyma tissue.
%\emph{KH} derived at the hypotheses: \emph{Somatometric features impose the major influences on the parenchyma tissue.}
%%

\textbf{Detailed Breast Parenchyma Analysis.}
%%
The analysis was conducted by calculating the cube $Parenchyma-Percentage \sim X + Y + Z$.
%%
Using the 3D cube, \emph{KH} observed several hotspots.
%%
Navigating to them using the slicing facility of the 3D visualization highlighted several features of high influence, such as image-derived features, as glandular tissue density, parenchyma segmentation metrics.
%%
Also, strong correlations were observed in the diabetes slice, confirming expectations of \emph{KH} w.r.t. to its strong influence to the parenchyma tissue.
%%
A surprising find were the strong correlations with kidney disorder ($R^2$ values around $0.9$).
%%
The \textbf{3.DD} analysis however showed only 8 subjects with kidney disorder.
%%
The finding was noted and investigated further in the near future using a extensive data set.
%%
Lastly \emph{KH} assessed the influence of contraception related features, such as use birth control pills or the spiral, but found no significant correlations with the parenchyma.
%%
Features, such as alcohol intake yield no elevated $R^2$ values.
%%
\emph{KH} remarked that these features are believed to have an impact on the parenchyma tissue, but they are less reliability since they are self-reported.
%%
%mamma anamnesis breast fed, contraception (spirale, pille), alcohol intake
%Lastly, \emph{KH} assessed the influence of image-derived features on the parenchyma tissue.
%%
%She observed expected results 
%Using the slicing mode to fast 
%Hypotheses
%Detailed analysis: Cholesterin, influence of image-derived feautres, classification of the BI-Rads (how well did the manual segmentation perform)
\subsection{Further Feedback and Lessons Learned} \label{Lessons Learned}
%%
Our method was well received among the domain experts.
%%
For the first time, they were able to derive an overview visualization custom tailored to underlying assumptions.
%%
In this context, \emph{TI} highlighted the ability to simultaneously analyze thousands of regression models while maintaining little time expenses for rating them.
%The novel way of modeling knowledge to derive hypothesis driven overview visualizations allow for detailed analysis of target features, either disease indicators or even image-derived features.
%%
%TI commented on the

\textbf{Extracted Hypotheses have to be investigated further.}
%%
Agreeing with \emph{TI}'s feedback, each finding and hypothesis has to be confirmed using a dedicated statistical analysis.
%%
An accompanying search for correlations potentially highlighting confounders can be carried out using our method.
%%
%This incorporates detailed investigation of potential confounder features as well as looking for outlier subjects.
%%
\emph{TI} commented on the possibility of adding more regression types to model different correlation types.% to customize the cube even more.
%%
%TI hinted the neccissity of different regression types, which also model non-linear relationships, but do not comprise of comparable quality-of-fit measures, such as the $R^2$.
%%
%\com{Tills Feedback - Regression analysis also incorporates assumptions about the data, }
%%

@@

% \com{Rewrite, focus on precise definition on what was done and why it is awesome.}
% We presented a technique for knowledge discovery in cohort study data sets with user-defined target features.
% %%
% \emph{Regression Cubes} are based on eponymous regression models, which allow to model domain knowledge about the data (e.g. influencing features on a disease) using formulas.
% %%
% Alternatively, \emph{Regression Cubes} can be calculated using default formulas to assess the explanatory power towards each feature in the data set.
% %%
% These two approaches allow both for a \emph{hypothesis-free} and \emph{hypothesis-based} explorative analysis.
% %%
% Correlation-based feature selection reduces the amount of calculations using the target feature by focusing on the important regression models.
% %%
% The prototype described in this work was developed using state of the art web technologies, free services and open source libraries.
% %%
% All code associated to this project is also open source.
% %%
% Two case studies revealed that the presented approach enables to reproduce knowledge extracted using decision-tree-based data mining methods on a hepatic steatosis data set, as well as producing new hypotheses by deriving insight into influencing factors on breast fat tissue in a explorative analysis.
% %%
%
% As future work, we want to introduce more regression models to the data set, which model different correlation types.
% %%
% We also want to extend the cube to time-dependent data by expanding the difference-cube approach.
% %%
%
% The method was very well received with our project partners, allowing them for the first time to retrieve an overview visualization of features, which does not highlights their pairwise correlations, but rather their explanatory power towards a target feature.
% %%
% The observed relationship are now subject of detailed statistical analyses.
% %%
% Our provided system not restricted to the epidemiological domain, using the provided instance, everybody can upload their own data or even set up their own \emph{Regression Cube} server cluster.
% %%
% We believe in the power of opening up knowledge discovery to allow a heterogenous group of domain experts to derive insight into their data and support the notion of open science.
%%
%%\paragraph{Future Work.}
%%\com{Implementing of regression analysis on the graphics card.}
%%
% \begin{small}
	%\acknowledgments{Omitted due to blind review}
\acknowledgments{SHIP is part of the Community Medicine Research net of the University of Greifswald, Germany, which is funded by the Federal Ministry of Education and Research (grant no. 03ZIK012), the Ministry of Cultural Affairs as well as the Social Ministry of the Federal State of Mecklenburg-West Pomerania. Whole-body MR imaging was supported by a joint grant from Siemens Healthcare, Erlangen, Germany and the Federal State of Mecklenburg-Vorpommern. The University of Greifswald is a member of the √¢¬Ä¬òCentre of Knowledge Interchange√¢¬Ä¬ô program of the Siemens AG. This work was supported by the DFG Priority Program 1335: Scalable Visual Analytics.}
% \end{small}
\clearpage
\newpage
\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{bibliography}
\end{document}

>>>>

We defined an Interactive Visual Analysis workflow for image-centric cohort study data, by extending the feature selection step (recall \ref{sec:Background}) with an iterative analysis loop incorporating group selection and visualization using expert input as well as clustering methods \cite{Klemm2014VIS}.
%%
Information visualizations of cohort study features were augmented with extracted image data, yielding linked views with both image and non-image information.
%% 
% erst die ErklâÂ§rung, dann die Folge daraus =)
The mosaic plot presented in \cite{Klemm2014VIS} highlights the pairwise correlation between features without a target disease by depicting the \emph{Cram\'{e}r's V} contingency values.
%%
Its great popularity among our domain experts was the inspiration for this work.
%%

@@

% nochmal checken wo $F$ eingefÂ¸hrt wird, hier oder im Â¸bernâ°chsten Satz?

@@

% Ggf. wurde $F$ schon oben eingefÂ¸hrt, TODO

@@

\paragraph{3D (Cube) View.}
%%
Introducing $Z$ creates a 3D \emph{Regression Cube} (Fig.~\ref{fig:Cube} b).
%%
$R^2$ values of each cube entry (\emph{voxel}) is mapped to opacity to reduce the overlap.
%%
The visualization of $R^2$ values derived from different regression cubes (e.g., $Z \sim X + Y$) is misleading, as they can be compared relatively, but not in precise numbers.
%%
% e.g. wenn man es wâ°hlen kann
% i.e. wenn es so ist
Therefore, the $R^2$ results of different regression methods are encoded using different colors (i.e., blue for linear regression and red for logistic regression).
%%
% Adverb immer vors Hauptverb oder Satzende
Thus, the cube can be easily extended using other regression types.
%%
For cubes with a fixed target feature, e.g., $Cancer \sim X + Y + Z$, no such encodings are required and the $z$ dimension can be compared directly.
%%
\\\\
Our goal is to create an overview visualization for a data set, but we also want to incorporate expert knowledge into the visualization by adapting the underlying formulas.
%%
These two approaches do not exclude each other, they rather underline the difference in purpose of the chosen formula.
%%
The different analysis approaches require different starting points using the \emph{Regression Cube}.

\subsection{Analysis Workflow} \label{sec:Workflow}
%%
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.0in]{figures/workflow}
 \caption{
 Different workflow types of the analysis using \emph{Regression Cubes} (based on~\cite{Keim}).
 %%
 % The analysis starts with a set of features given by the data set.
 %%
 [\textbf{1.AF}] The workflow starts by declaring a formula regarding to specify a hypothesis, or use a predefined formula for a hypothesis-free analysis.
 %%
 [\textbf{2.SI}] The \emph{Regression Cube} is then visualized.
 %%
 The user has the option to either adjust the formula or to derive details on demand on a specific regression.
 %%
 [\textbf{3.ZF}] Insights into the data yield either an adjustment of the current formula or selecting a difference view.
 %%
 The latter is used to compare regression cubes.
 %%
 [\textbf{4.DD}] Details about features using the 2D mosaic plot representation yields insights and hypothesis about feature relations.
 }
  \label{fig:Workflow}
\end{figure}
%%
%\com{Different Formulas work as different steps in the analysis (Fig.~\ref{fig:Workflow})}
%\com{Workflow for different analysis approaches.}
%\com{0. Select the Variables.}
%\com{1. Select the Formulas}
%\com{a) Analysis without hypothesis about the data set (z ~ x+y)}
%\com{b) Analysis without hypothesis with confounder (z ~ age)}
%\com{c) Analysis with hypothesis about the data set (Var ~ x+y+z)}
%\com{d) Use Difference View}
%\com{d) Clarify using confounder (Var ~ x)}
%\com{3. Find interesting pane.}
%\com{4. Get Details on Demand.}
%%
% â¹bergang ist recht holprig gewesen
Our Regression Cube models is well-suited for different workflow analysis techniques, based on the Visual Analytics (VA) Mantra of Keim et al. \cite{Keim}:

@@

% warum war da ein "either", sollte der Satz etwas anderes ausdrÂ¸cken?
Hypotheses about the data are easily built up by relating dynamic variables with the regression operators.
%%
Furthermore, static features can be added for each regression formula.
%%
Here are a few examples:

@@

\section{Application} \label{application}
%%
\begin{figure*}[htb]
 \centering
 \includegraphics[width=7.0in]{figures/application}
 \caption{
 The analysis of the numerical and dichotomized target feature depicting liver-fat values yields similar results (left).
 %%
 In (a), hot spots for somatometrical features with high correlations were found.
 %%
 High correlations were also found for features depicting \emph{hepatic steatosis} (b).
 %%
 A high correlation between \emph{Interleukin-6}, \emph{hepatic steatosis}, \emph{GGT} and \emph{Lipase} (highlighted using arrows) was revealed during the analysis using the 2D mosaic plot.
 %%
 The hypothesis-free analysis of the breast fat data set (right) towards the \emph{parenchyma tissue percentage} of the breast displays correlations between \emph{age}, \emph{body fat}, \emph{hip circumference} as well as \emph{menstrual period}.
 }
  \label{fig:Application}
\end{figure*}
%%
In this section, we describe how we applied the \emph{Regression Cube} to two epidemiological data sets.
%%
The hepatic steatosis data set was analyzed using data mining algorithms, yielding risk groups, which we now analyze further.
%%
Also, we try to reproduce the prior results from this analysis as proof-of-concept of our method.
%%
The breast fat data set is the foundation for an explorative analysis towards the influencing parameters of the parenchyma tissue of the female breast.
%%

@@

The \textbf{1.AF} was started by \emph{KH} using the default formula for hypothesis-free analysis ($Z \sim X + Y$).
%%
At first, she was interested in correlations with the \emph{parenchyma tissue} percentage, which was selected through the drop-down for the z-axis (\textbf{2.SI}).
%%
She observed strong correlations with \emph{age}, \emph{body fat percentage}, \emph{hip} and \emph{waist circumference} as well as \emph{menstrual period} or \emph{pregnancy status} as expected (Fig.~\ref{fig:Application} right).
%%
Women with higher \emph{body fat} also have a larger \emph{breast fat percentage}, which also correlates with other somatometric features.
%%
\emph{Age} is a strong influencing factor, as breast tissue and subsequently the parenchyma tissue degrades over time.
%%
\emph{KH} proceeded using \textbf{2.SI} and \textbf{3.DD} to check for relationships for different target features, such as current \emph{hormone replacement therapy}, \emph{BI-RADS} (classification of the mammography findings) as well as different diseases, such as \emph{diabetes} or \emph{gout}.
%%
She observed relationships matching her expectations and expert knowledge.
%%
One unexpected relationship was observed between \emph{breast lesions} and \emph{menstruation cycle} towards \emph{spiral contraception} ($R^2$ of $0.77$).
%%
\emph{KH} proceeded with a detailed analysis of the parenchyma tissue.
%\emph{KH} derived at the hypotheses: \emph{Somatometric features impose the major influences on the parenchyma tissue.}
%%

\textbf{Detailed Breast Parenchyma Analysis.}
%%
The analysis was conducted by calculating the cube $Parenchyma\_Percentage \sim X + Y + Z$.
%%
Using the 3D cube, \emph{KH} observed several hotspots.
%%
Navigating to them using the slicing facility of the 3D visualization highlighted features of high influence, such as image-derived features, as \emph{glandular tissue density} and \emph{parenchyma segmentation} metrics.
%%
Also, strong correlations were observed in the \emph{diabetes} slice, confirming expectations of \emph{KH} w.r.t. to its strong influence to the parenchyma tissue.
%%
A surprising find were the strong correlations with \emph{kidney disorder} ($R^2$ values around $0.9$).
%%
The \textbf{3.DD} analysis however showed only 8 subjects with \emph{kidney disorder}.
%%
Too few subjects impose the risk of a biased finding.
%%
The correlation was noted and will be investigated further in the near future using a extensive data set.
%%
Lastly \emph{KH} assessed the influence of contraception related features, such as use \emph{birth control pills} or the \emph{spiral}, but found no significant correlations with the parenchyma tissue.
%%
Other consumption behavior features, such as \emph{alcohol intake} also yield no elevated $R^2$ values.
%%
\emph{KH} remarked that these features are believed to have an impact on the parenchyma tissue, but they are less reliability since they are self-reported.
%%
%mamma anamnesis breast fed, contraception (spirale, pille), alcohol intake
%Lastly, \emph{KH} assessed the influence of image-derived features on the parenchyma tissue.
%%
%She observed expected results 
%Using the slicing mode to fast 
%Hypotheses
%Detailed analysis: Cholesterin, influence of image-derived feautres, classification of the BI-Rads (how well did the manual segmentation perform)
\subsection{Further Feedback and Lessons Learned} \label{Lessons Learned}
%%
Our method was well received among the domain experts.
%%
For the first time, they were able to derive an overview visualization custom tailored to underlying assumptions.
%%
\emph{KH} noted the ease of use, which "\emph{converts data sets into a feasible form}".
%%
She highlighted the efficiency of combining fast target feature selection with visually highlighting interesting results, enabling rapid analysis cycles.
%%
To get nearly similar results she would had to spend hours using \texttt{SPSS} and also might have missed many interesting hot spots during this process.
%She noted that she usually would have to spend hours using \texttt{SPSS} to assess the data in the detail we presented.
%%
\emph{TI} highlighted the ability to simultaneously analyze thousands of regression models while maintaining little time expenses for rating them.
%The novel way of modeling knowledge to derive hypothesis driven overview visualizations allow for detailed analysis of target features, either disease indicators or even image-derived features.
%%
%TI commented on the

\textbf{Extracted Hypotheses have to be investigated further.}
%%
%Our method combines powerful statistical techniques with 
We map results of complex statistical results into comprehensive visualizations.
%%
Agreeing with \emph{TI}'s feedback, each finding and hypothesis has to be confirmed using a dedicated statistical analysis.
%%
An accompanying search for correlations potentially highlighting confounders can be carried out using our method.
%%
Statistical validation of an epidemiological end result still has to be carried out by statisticians using their respective tools.
%%
%This incorporates detailed investigation of potential confounder features as well as looking for outlier subjects.
%%
\emph{TI} commented on the possibility of adding more regression types to model different correlation types.% to customize the cube even more.
%%
%TI hinted the neccissity of different regression types, which also model non-linear relationships, but do not comprise of comparable quality-of-fit measures, such as the $R^2$.
%%
%\com{Tills Feedback - Regression analysis also incorporates assumptions about the data, }
%%

@@

% \com{Rewrite, focus on precise definition on what was done and why it is awesome.}
% We presented a technique for knowledge discovery in cohort study data sets with user-defined target features.
% %%
% \emph{Regression Cubes} are based on eponymous regression models, which allow to model domain knowledge about the data (e.g. influencing features on a disease) using formulas.
% %%
% Alternatively, \emph{Regression Cubes} can be calculated using default formulas to assess the explanatory power towards each feature in the data set.
% %%
% These two approaches allow both for a \emph{hypothesis-free} and \emph{hypothesis-based} explorative analysis.
% %%
% Correlation-based feature selection reduces the amount of calculations using the target feature by focusing on the important regression models.
% %%
% The prototype described in this work was developed using state of the art web technologies, free services and open source libraries.
% %%
% All code associated to this project is also open source.
% %%
% Two case studies revealed that the presented approach enables to reproduce knowledge extracted using decision-tree-based data mining methods on a hepatic steatosis data set, as well as producing new hypotheses by deriving insight into influencing factors on breast fat tissue in a explorative analysis.
% %%
%
% As future work, we want to introduce more regression models to the data set, which model different correlation types.
% %%
% We also want to extend the cube to time-dependent data by expanding the difference-cube approach.
% %%
%
% The method was very well received with our project partners, allowing them for the first time to retrieve an overview visualization of features, which does not highlights their pairwise correlations, but rather their explanatory power towards a target feature.
% %%
% The observed relationship are now subject of detailed statistical analyses.
% %%
% Our provided system not restricted to the epidemiological domain, using the provided instance, everybody can upload their own data or even set up their own \emph{Regression Cube} server cluster.
% %%
% We believe in the power of opening up knowledge discovery to allow a heterogenous group of domain experts to derive insight into their data and support the notion of open science.
%%
%%\paragraph{Future Work.}
%%\com{Implementing of regression analysis on the graphics card.}
%%
% \begin{small}
	%\acknowledgments{Omitted due to blind review}
\acknowledgments{SHIP is part of the Community Medicine Research net of the University of Greifswald, Germany, which is funded by the Federal Ministry of Education and Research (grant no. 03ZIK012), the Ministry of Cultural Affairs as well as the Social Ministry of the Federal State of Mecklenburg-West Pomerania. Whole-body MR imaging was supported by a joint grant from Siemens Healthcare, Erlangen, Germany and the Federal State of Mecklenburg-Vorpommern. The University of Greifswald is a member of the ‘Centre of Knowledge Interchange’ program of the Siemens AG. This work was supported by the DFG Priority Program 1335: Scalable Visual Analytics. This work was supported by the federal state of Saxony-Anhalt under grant number 'I 60' within the Forschungscampus STIMULATE.}
% \end{small}
\clearpage
\newpage
\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{bibliography}
\end{document}
